Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-02 SI.tex
Add figures up to figure 5

Here we will show the results of dielectric properties calculated
using many-body Green function method (G$_0$W$_{0}$) and with
electron-hole interactions at the level of the Bethe-Salpeter equation
(G$_0$W$_{0}$--BSE). Frequency-dependent dielectric functions
$\varepsilon_{\mathrm{SL}}(\omega)$ at both G0W0 and G0W0--BSE levels
are calculated using VASP, with a cutoff energy of XXX and k point
density of YYY. Local field effect is included in both cases: local
field correction is applied to independent-particle energies in G0W0
at RPA level with VASP TAG \texttt{LRPA=.TRUE.}, while the full
polarizability is calculated using BSE in G0W0-BSE
\todo[inline]{@Declan, could you help modify this part?}

>>>>

Here we will show the results of dielectric properties calculated
using many-body Green function method (G$_{0}$W$_{0}$) and with
electron-hole interactions at the level of the Bethe-Salpeter equation
(G$_{0}$W$_{0}$–BSE). Frequency-dependent dielectric functions,
$\varepsilon_{\mathrm{SL}}(L)$, were calculated at the level of
G$_{0}$W$_{0}$ and G$_{0}$W$_{0}$+BSE levels using VASP. For the
calculations on G$_{0}$W$_{0}$, a 12$\times$12$\times$1 $\Gamma$-centered k-grid was
used along with an 800 eV energy cutoff in the plane waves and in
calculation of the response function. 120 bands (4 occupied and 116
unoccupied) were used in the calculation of
$\varepsilon_{\mathrm{SL}}(\omega)$ of monolayer BN, with local-field
effects being included on the RPA level. For the calculation of the
Bethe-Salpeter equation, the Tamm-Dancoff approximation was used with
two occupied and two unoccupied bands being included in the
calculation.

% Here we will show the results of dielectric properties calculated
% using many-body Green function method (G$_0$W$_{0}$) and with
% electron-hole interactions at the level of the Bethe-Salpeter equation
% (G$_0$W$_{0}$--BSE). Frequency-dependent dielectric functions
% $\varepsilon_{\mathrm{SL}}(\omega)$ at both G0W0 and G0W0--BSE levels
% are calculated using VASP, with a cutoff energy of XXX and k point
% density of YYY. Local field effect is included in both cases: local
% field correction is applied to independent-particle energies in G0W0
% at RPA level with VASP TAG \texttt{LRPA=.TRUE.}, while the full
% polarizability is calculated using BSE in G0W0-BSE
% \todo[inline]{@Declan, could you help modify this part?}

### 2019-10-02 paper.tex
Add figures up to figure 5

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  as superimposed on \textbf{c} and \textbf{d}.}
\end{figure}

\begin{table}[H]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & 45.5 & 2.72  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha_{\mathrm{2D}}^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) functionals.}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
  \caption{\label{fig-emt} \textbf{Failure of the effective 2D
      ``dielectric constant'' picture based on the effective medium
      theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
    effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
    is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
    the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
    not well-defined. \textbf{b}.  Estimation error between
    $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
    $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
    of /ab initio/ $\varepsilon_{\mathrm{SL}} - L$ data for selected
    2D metal dichacolgenides. The uncertainty of
    $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
    $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
    particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  and Ref.~\cite{Mounet_2018} (triangles) as superimposed on
  \textbf{c} and \textbf{d}.}
\end{figure}

% \begin{table}[H]
%   \centering
%   \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
%     ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
%     selected 2D materials calculated from first principles
%     simulations. $r_{0}^{\parallel}$ is in general much larger than
%     $r_{0}^{\perp}$, which accounts for the highly anisotropic
%     dielectric nature of 2D materials.}
%   \label{tbl:radii}  
%   \begin{tabular}{lcc}
%     \hline
%     Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
%     \hline
%     2H-MoS$_{2}$ & 40.0 & 2.50 \\
%     2H-MoSe$_{2}$ & 45.5 & 2.72  \\
%     2H-MoTe$_{2}$ & 58.1 & 3.07  \\
%     2H-WS$_{2}$ & 35.7 & 2.46  \\
%     2H-WSe$_{2}$ & 41.0 & 2.71 \\
%     2H-WTe$_{2}$ & 53.5 &  3.17\\
%     \hline
%   \end{tabular}
% \end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
\caption{\label{fig-4} \textbf{Application of 2D polarizability to
    multilayer and 3D systems}.  \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart.  By applying the concept of
  electronic polarizability to multilayer 2D materials, the multilayer
  polarizabilities $\alpha_{\mathrm{NL}}^{\parallel}$ and
  $\alpha_{\mathrm{NL}}^{\perp}$ of selected 2D metal dichacolgenides
  as functions of number of layers $N$ are shown in \textbf{a} and
  \textbf{b}, respectively. Both $\alpha_{\mathrm{NL}}^{\parallel}$
  and $\alpha_{\mathrm{NL}}^{\perp}$ linearly scales with $N$ and the
  electronic polarizabilities of monolayer, indicating that
  $\alpha_{\mathrm{2D}}$ is an additive quantity under weak
  interacting regime. The 2D to 3D transition is further studied in
  \textbf{c} and \textbf{d}, where $\alpha_{\mathrm{2D}}$ of an
  monolayer 2D material is compared with its bulk counterpart
  $\varepsilon_{\mathrm{Bulk}}$. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good
  correlation. \textbf{d} $\varepsilon_{\mathrm{bulk}}^{\perp}$
  calculated from DFT (y-axis) compared with the predicted value from
  2D $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis). The predicted value
  is in good aggreement with the DFT calculation when
  $E_{\mathrm{g}}>4$ eV, due to minimal interlayer coupling. The
  comparisons in \textbf{b} and \textbf{c} are made based on both
  HSE06 (circles) and PBE (squares) functionals.}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width-0.8\linewdith]{img/fig-ellipsoid.pdf}
  \caption{\label{fig-ellip} \textbf{Geometric representation of the
      2D polarizability}. \textbf{a}. Scheme of the polarizability
    ellipsoid of a 2D material, with its in-plane
    ($r_{0}^{\parallel}$) and out-of-plane radii
    ($r_{\mathrm{0}}^{\perp}$) proportional to
    $\alpha_{\mathrm{2D}}^{\parallel}$ and
    $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  The values of
    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D metal
    dichalcogenides are shown in \textbf{b} and \textbf{c},
    respectively.  }
\end{figure}
